Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-30 Paper1.tex
Changed figures and quick typos fixing

Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE. However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are at least two orders of magnitude smaller than the diagonal ones}. 
Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}. The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

@@

We start with the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.

@@

For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
In this range both DE and II can occur in principle. The height of the peak is approximately the same for both $v$, despite both hybridizations differing by a factor of two. The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$. For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$. This, together with the comparable magnitude of the current maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial amount of II processes take place, while these are absent or negligible for $v=0.8$.
Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.

@@

We now discuss the effect of coupling to acoustic phonons on these results.

The current $j$ in presence of phonons shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slighty larger than the EO one for $\Omega\lesssim7$. This effect is reduced with increasing $\Omega$ until a crossing occurs at $\Omega\approx7$ where the EO current overtakes. Between $7\lesssim\Omega\lesssim14$, the current in the presence of phonons exhibits the same qualitative behavior as the EO one, reaching its maximum at $\Omega\approx 11$. However the current magnitude is suppressed, especially around the peak. For $\Omega\gtrsim14$ the current with phonons goes down as for the EO case.

The double occupation $N_{\text{D}}$  shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) is larger than and follows the behavior of its EO counterpart within the entire $\Omega$-range considered.
The spectral and occupation functions  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap. Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as the occupation function shows.
 The spectral function in presence of phonons is  broadened and tends to fill the pseudogap $\Delta_{\text{pg}}$ as anticipated in Sec.~\ref{sec:scheme_electrons_phonons}.
This reduction of the pseudogap explains why the current in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slightly larger in presence of phonons for $\Omega\lesssim7$. With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency $\Omega$ thereby increasing the photocurrent. On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, see Fig. \ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.

@@

\section*{Acknowledgements}

>>>>

Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE. However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed with respect to the diagonal ones}. 
Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}. The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

@@

We set off by analyzing the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.

@@

For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
In this range both DE and II can occur in principle. The height of the peak is approximately the same for both $v$, despite the hybridizations differ by a factor of two. The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$. For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$. This, together with the comparable magnitude of the current maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial amount of II processes take place, while these are absent or negligible for $v=0.8$.
Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.

@@

We now discuss the effect of coupling to acoustic phonons on the results presented thus far.

The current $j$ in presence of phonons shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slighty larger than the EO one for $\Omega\lesssim7$. This effect is reduced with increasing $\Omega$ until a crossing occurs at $\Omega\approx7$ where the EO current overtakes. Between $7\lesssim\Omega\lesssim14$, the current in the presence of phonons exhibits the same qualitative behavior as the EO one, reaching its maximum at $\Omega\approx 11$. However the current magnitude is suppressed, especially around the peak. For $\Omega\gtrsim14$ the current in presence of phonons drops as for the EO case.

The double occupation $N_{\text{D}}$  shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) is larger than and follows the behavior of its EO counterpart within the entire $\Omega$-range considered.
The spectral and occupation functions  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap. Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as evidenced by the occupation function.
 The spectral function in presence of phonons is  broadened and tends to fill the pseudogap $\Delta_{\text{pg}}$ as anticipated in Sec.~\ref{sec:scheme_electrons_phonons}.
This reduction of the pseudogap explains why the current in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slightly larger in presence of phonons for $\Omega\lesssim7$. With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency $\Omega$ thereby increasing the photocurrent. On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, see Fig. \ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.

@@

\acknowledgments

### 2022-08-30 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
Last version paper 30.08.2022
Changed figures and quick typos fixing

%%%%%%%%%%%%
% PGFPLOTS %
%%%%%%%%%%%%
\usepackage{pgfplots}    % pgfplots 
\usepackage{tikz-3dplot} % 3D coordinate frames
\usepackage{gnuplot-lua-tikz}
\usepgfplotslibrary{fillbetween}
\usepgfplotslibrary{colormaps}
\pgfplotsset{compat=1.17}
% \pgfplotsset{trig format plots=rad}

@@

% foreground, background
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfdeclarelayer{main} 
\pgfsetlayers{background,main,foreground}

@@

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
ylabel={$A(\omega)$},
legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill, 
    precision=0, 
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{el};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{el+ph};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

@@

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};

>>>>

%%%%%%%%%%%%
% PGFPLOTS %
%%%%%%%%%%%%
\usepackage{pgfplots}    % pgfplots 
\usepackage{tikz-3dplot} % 3D coordinate frames
%\usepackage{gnuplot-lua-tikz}                                % macOS does not like it -> restore if commenting it out gives you troubles
\usepgfplotslibrary{fillbetween}
\usepgfplotslibrary{colormaps}
\pgfplotsset{compat=1.17}
% \pgfplotsset{trig format plots=rad}

@@

% foreground, background
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfdeclarelayer{main} 
\pgfsetlayers{background,main,foreground}
\pgfplotsset{tick scale binop=\times}

@@

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
ylabel={$A(\omega)$},
legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
yticklabels={\smash{\raisebox{0.1\height}{0}},3,6,\smash{\raisebox{-0.8\height}{9}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill, 
    precision=0, 
    /tikz/.cd}
]

%\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
%\addlegendentry{el};
%\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
%\addlegendentry{el+ph};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$v=0.4$};

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-16.0,0.06)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

@@

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$v=0.8$};

### 2022-08-30 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Last version paper 30.08.2022
Changed figures and quick typos fixing

%%%%%%%%%%%%
% PGFPLOTS %
%%%%%%%%%%%%
\usepackage{pgfplots}    % pgfplots 
\usepackage{tikz-3dplot} % 3D coordinate frames
\usepackage{gnuplot-lua-tikz}
\usepgfplotslibrary{fillbetween}
\usepgfplotslibrary{colormaps}
\pgfplotsset{compat=1.17}
% \pgfplotsset{trig format plots=rad}

@@

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
ylabel={$A(\omega)$},
legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0, 
    /tikz/.cd}
]

@@

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=5$};

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=11$};

>>>>

%%%%%%%%%%%%
% PGFPLOTS %
%%%%%%%%%%%%
\usepackage{pgfplots}    % pgfplots 
\usepackage{tikz-3dplot} % 3D coordinate frames
%\usepackage{gnuplot-lua-tikz}                     % macOS does not like it -> restore if you need it
\usepgfplotslibrary{fillbetween}
\usepgfplotslibrary{colormaps}
\pgfplotsset{compat=1.17}
% \pgfplotsset{trig format plots=rad}

@@

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
ylabel={$A(\omega)$},
legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
 yticklabels={\smash{\raisebox{0.1\height}{0}},3,6,\smash{\raisebox{-0.8\height}{9}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0, 
    /tikz/.cd}
]

%\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
%\addlegendentry{$v=0.4$};
%\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
%\addlegendentry{$v=0.8$};

@@

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$\Omega=5$};

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-22.0,0.034)},anchor=west,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$\Omega=11$};
